Monitoring Forest Health Using Hyperspectral Imagery: Does Feature Selection Improve the Performance of Machine-\linebreak Learning Techniques?

### 2021-12-17 docs/00-manuscripts/mdpi/submissions/proofreading-before-pub/remotesensing-1398065 english editing done.tex
add assets of all submissions

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0003-0748-6624} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-7834-4717} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0003-2567-8689} % Add \orcidC{} behind the author's name
\newcommand{\orcidauthorD}{0000-0002-6390-5873} % Add \orcidD{} behind the author's name
\newcommand{\orcidauthorE}{0000-0001-6002-6980} % Add \orcidE{} behind the author's name
\newcommand{\orcidauthorF}{0000-0001-6640-679X} % Add \orcidF{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Patrick Schratz $^{1,}$*\orcidA{}, Jannes Muenchow $^{1}$\orcidB{}, Eugenia Iturritxa $^{2}$\orcidD{}, José Cortés $^{1}$\orcidC{}, Bernd Bischl $^{3}$\orcidE{} and~Alexander~Brenning $^{1}$\orcidF{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad GIScience Group, Department of Geography, Friedrich Schiller University Jena, Germany;
 malnamalja@gmx.de~(J.M.); jose.cortes@uni-jena.de~(J.C.); alexander.brenning@uni-jena.de~(A.B.)\\
$^{2}$ \quad NEIKER Tecnalia, Spain; eiturritxa@neiker.eus\\
$^{3}$ \quad Department of Statistics, Ludwig-Maximilians-Universität München, Germany; bernd.bischl@stat.uni-muenchen.de
}

@@

The \textit{Pinus radiata} plots of this study, namely Laukiz1, Laukiz2, Luiando, and Oiartzun, are located in the northern part of the Basque Country (Figure~\ref{fig:study_area}).
Oiartzun has the largest number of observations ($n = 559$ trees), while Laukiz2 is the largest in area (1.44~ha).
All plots besides Luiando are located within 100~km from the coast (Figure~\ref{fig:study_area}).
A total of 1808~observations are available (Laukiz1: 559, Laukiz2: 451, Luiando: 301, Oiartzun: 497).
Field surveys were conducted in September 2016 by experienced forest pathologists.
Defoliation was measured in 5\% steps through visual inspection with the help of a score card.
For Laukiz2, values at three height levels (bottom, mid, and top) were available and averaged into an overall defoliation value, resulting in values that are not multiples of 5\% (e.g., 8.33\%).
The magnitude of human observer errors in such surveys, including the present one, is not precisely known and has being discussed for many years~\cite{innes1993}.
Ref.~\cite{maclean1982} estimated human observer errors in defoliation surveys to range between 7\% and 18\%.

@@

In total, the benchmarking grid consisted of 156 experiments (6 feature sets $\times$ 3~ML algorithms $\times$ 8 feature-selection methods and for the L1/L2 models, 6 feature sets~$\times$~2~models.
The selected hyperparameter settings are shown in Appendix~\ref{appendixA} Table~\ref{tab:hyperparameter_limits}.
All code and data are included in the research compendium of this study (\url{https://doi.org/10.5281/zenodo.2635403} (accessed on 27 November 2021).

@@

The algorithm implementations of the following packages were used: xgboost~\cite{chen2016} (extreme gradient boosting), kernlab~\cite{kernlab} (support vector machine) and glmnet~\cite{glmnet} (penalized regression).
The filter implementations of the following packages were used: praznik~\cite{praznik} and FSelectorRcpp~\cite{fselectorrcpp}.
Package mlr~\cite{mlr} was used for all modeling related steps, and drake~\cite{drake} was used for structuring the work and for reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}, (accessed on 27 November 2021).
Apart from the availability of code and manuscript sources, a static webpage is available at \url{https://pat-s.github.io/2019-feature-selection} (accessed on 27 November 2021) which includes additional side analyses that were carried out during the creation of this study.

@@

% - RMSE around 27
% - MBO tuned penalized methods are substantially worse
Overall, the response variable \enquote{tree defoliation} could be modeled with an \ac{RMSE} of 28 percentage points (p.p.) (Figure~\ref{fig:perf-result}).
SVM showed almost no differences in RMSE across feature sets whereas other learners (RF, SVM, XGBoost, lasso and ridge) differed up to five p.p. (Figure~\ref{fig:perf-result}).
SVM showed the best overall performance with a mean difference of around three p.p. to the next best model (XGBoost) (Table~\ref{tab:best-learner-perf}).
Performance differences between test folds were large: Predicting on Luiando resulted in an RMSE of 9.0 p.p. for learner SVM (without filter) but up to 54.3 p.p. when testing on Laukiz2 (Table~\ref{tab:svm-single-fold-perf}).

@@

\dataavailability{The data presented in this study are openly available in Zenodo at \url{https://doi.org/10.5281/zenodo.2635403} (accessed on 27 November 2021).}

\acknowledgments{We acknowledge support by the German Research Foundation and the Open Access Publication Fund of the Thueringer Universitaets- und Landesbibliothek Jena Projekt-Nr. 433052568.}

@@

		\bfseries{Name} & \bfseries{Formula}                                                                                   & \bfseries{Reference~}

@@

		GDVI            & $(R_{800}^n-R_{680}^n) / (R_{800}^n+R_{680}^n)$  &~\cite{wu2014}                 \\

@@

\bibitem[Thenkabail \em{et~al.}(2018)Thenkabail, Lyon, and
  Huete]{thenkabail2018}
Thenkabail, P.S.; Lyon, J.G.; Huete, A. (Eds.)
\newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
  and Vegetation}; {CRC Press}:  Boca Raton, FL, USA, 2018, doi:10.1201/9781315159331.

@@

\bibitem[Lin \em{et~al.}(2014)Lin, Yan, Wang, and Song]{lin2014}
Lin, H.; Yan, E.; Wang, G.; Song, R.
\newblock Analysis of Hyperspectral Bands for the Health Diagnosis of Tree
  Species.
\newblock  In Proceedings of the 2014 {{Third International Workshop}} on {{Earth Observation}} and
  {{Remote Sensing Applications}} ({{EORSA}}), Changsha, China, 11--14 June 2014; pp. 448--451, doi:10.1109/EORSA.2014.6927931.

@@

\bibitem[Trunk(1979)]{trunk1979}
Trunk, G.V.
\newblock A {{Problem}} of {{Dimensionality}}: A {{Simple Example}}.
\newblock {\em IEEE Trans. Pattern Anal. Mach. Intell.}
  {\bf 1979}, {\em PAMI-1}, 306--307.

@@

\bibitem[Innes(1993)]{innes1993}
Innes, J.
\newblock Methods to Estimate Forest Health.
\newblock {\em Silva Fenn.} {\bf 1993}, {\em 27}, doi:10.14214/sf.a15668.

@@

\bibitem[Das(2001)]{das2001}
Das, S.
\newblock \emph{Filters, {{Wrappers}} and a {{Boosting}}-{{Based Hybrid}} for
  {{Feature Selection}}};
\newblock  {{ICML}}, Citeseer, 2001.

@@

\bibitem[Dietterich(2000)]{dietterich2000}
Dietterich, T.G.
\newblock Ensemble {{Methods}} in {{Machine Learning}}.
\newblock  In Proceedings of the {{First International Workshop}} on {{Multiple
  Classifier Systems}}, Cagliari, Italy, 21--23 June 2000; {Springer}:  Berlin/Heidelberg, Germany,
 2000; pp. 1--15.

@@

\bibitem[Feurer \em{et~al.}(2015)Feurer, Klein, Eggensperger, Springenberg,
  Blum, and Hutter]{feurer2015}
Feurer, M.; Klein, A.; Eggensperger, K.; Springenberg, J.; Blum, M.; Hutter, F.
\newblock Efficient and {{Robust Automated Machine Learning}}. In {\em Advances
  in {{Neural Information Processing Systems}} 28}; Cortes, C., Lawrence, N.D.,
  Lee, D.D., Sugiyama, M., Garnett, R., Eds.; {Curran Associates, Inc.}:  2015;
  pp. 2962--2970.

@@

\bibitem[Zuber and Strimmer(2011)]{zuber2011}
Zuber, V.; Strimmer, K.
\newblock High-{{Dimensional Regression}} and {{Variable Selection Using CAR
  Scores}}.
\newblock {\em Stat. Appl. Genet. Mol. Biol.} {\bf
  2011}, {\em 10}, 1-27, doi:10/c62xhp.

\bibitem[Kira and Rendell(1992)]{kira1992}
Kira, K.; Rendell, L.A.
\newblock The Feature Selection Problem: Traditional Methods and a New
  Algorithm.
\newblock  In Proceedings of the Tenth National Conference on {{Artificial}}
  Intelligence, San Jose, CA, USA, 12--16 July 1992; {AAAI Press}:  1992; pp. 129--134.

@@

\bibitem[Brenning(2012)]{sperrorest}
Brenning, A.
\newblock Spatial Cross-Validation and Bootstrap for the Assessment of
  Prediction Rules in Remote Sensing: The {{R}} Package Sperrorest.
\newblock  In Proceedings of the 2012 {{IEEE International Geoscience}} and {{Remote Sensing
  Symposium}}, Munich, Germany, 22--27 July 2012; {R} Package Version 2.1.0; {IEEE}:  2012,
\newblock
  doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/igarss.2012.6352393}{\detokenize{10.1109/igarss.2012.6352393}}}.

@@

\bibitem[Molnar(2019)]{molnar2019}
Molnar, C.
\newblock {\em Interpretable Machine Learning---{{A Guide}} for {{Making Black
  Box Models Explainable}}}; self-published: Munich, Germany, 2019.

@@

\bibitem[{R Core Team}(2019)]{rcoreteam2019}
{R Core Team}.
\newblock {\em R: A {{Language}} and {{Environment}} for {{Statistical
  Computing}}};  R Core Team: 2019, Vienna, Austria.

\bibitem[Chen and Guestrin(2016)]{chen2016}
Chen, T.; Guestrin, C.
\newblock {{XGBoost}}: A {{Scalable Tree Boosting System}}.
\newblock  In Proceedings of the {{22nd ACM SIGKDD International Conference}} on
  {{Knowledge Discovery}} and {{Data Mining}}, {{KDD}} '16, San Francisco, CA, USA, 13--17 August 2016; {ACM}: {New York, NY, USA},
  2016; pp. 785--794, doi:10.1145/2939672.2939785.

@@

\bibitem[Kursa(2018)]{praznik}
Kursa, M.B.
\newblock {\em Praznik: Collection of {{Information}}-{{Based Feature Selection
  Filters}}};  2018.

\bibitem[Zawadzki and Kosinski(2019)]{fselectorrcpp}
Zawadzki, Z.; Kosinski, M.
\newblock {\em {{FSelectorRcpp}}: '{{Rcpp}}' {{Implementation}} of
  '{{FSelector}}' {{Entropy}}-{{Based Feature Selection Algorithms}} with a
  {{Sparse Matrix Support}}};  2019.

@@

\bibitem[Landau(2018)]{drake}
Landau, W.M.
\newblock The {drake} {{R}} Package: A Pipeline Toolkit for Reproducibility and
  High-Performance Computing.
\newblock {\em J. Open Source Softw.} {\bf 2018}, {\em 3}.

@@

\bibitem[Lehnert \em{et~al.}(2016)Lehnert, Meyer, and Bendix]{lehnert2016}
Lehnert, L.W.; Meyer, H.; Bendix, J.
\newblock {\em Hsdar: Manage, Analyse and Simulate Hyperspectral Data in
  {{R}}};  2016.

@@

\bibitem[Rengarajan and Schott(2016)]{rengarajan2016}
Rengarajan, R.; Schott, J.R.
\newblock Modeling Forest Defoliation Using Simulated {{BRDF}} and Assessing
  Its Effect on Reflectance and Sensor Reaching Radiance.
\newblock  In \emph{Remote {{Sensing}} and {{Modeling}} of {{Ecosystems}} for
  {{Sustainability XIII}}}; {International Society for Optics and Photonics}:
  2016; San Diego, California, United States, Volume 9975, p. 997503, doi:10.1117/12.2235391.

@@

\bibitem[Rochac and Zhang(2016)]{rochac2016}
Rochac, J.F.R.; Zhang, N.
\newblock Feature Extraction in Hyperspectral Imaging Using Adaptive Feature
  Selection Approach.
\newblock  In Proceedings of the 2016 {{Eighth International Conference}} on {{Advanced Computational
  Intelligence}} ({{ICACI}}),  Chiang Mai, Thailand, 14--16 February 2016; pp. 36--40, doi:10.1109/ICACI.2016.7449799.

@@

\bibitem[Keller \em{et~al.}(2016)Keller, Braun, Hinz, and Weinmann]{keller2016}
Keller, S.; Braun, A.C.; Hinz, S.; Weinmann, M.
\newblock Investigation of the Impact of Dimensionality Reduction and Feature
  Selection on the Classification of Hyperspectral {{EnMAP}} Data.
\newblock  In Proceedings of the 2016 8th {{Workshop}} on {{Hyperspectral Image}} and {{Signal
  Processing}}: Evolution in {{Remote Sensing}} ({{WHISPERS}}),  Los Angeles, CA, USA, 21--24 August 2016; pp. 1--5, doi:10.1109/WHISPERS.2016.8071759.

@@

\bibitem[Walthall \em{et~al.}(1994)Walthall, Daughtry, Chappelle, Mcmurtrey,
  and Kim]{walthall1994}
Walthall, C.L.; Daughtry, C.S.T.; Chappelle, E.W.; Mcmurtrey, J.E.; Kim, M.S.
\newblock \emph{The {{Use}} of {{High Spectral Resolution Bands}} for {{Estimating
  Absorbed Photosynthetically Active Radiation}} ({{A Par}})}; NASA Gov, Washington, { 1994}.

@@

\bibitem[Chen(1996)]{chen1996}
Chen, J.M.
\newblock Evaluation of Vegetation Indices and a {{Modified Simple Ratio}} for
  Boreal Applications;
\newblock {\emph{Canadian Journal of Remote Sensing}}:  1996, \emph{22}, 229-242, doi:10.4095/218303.

@@

\bibitem[Guyot and Baret(1988)]{guyot1988}
Guyot, G.; Baret, F.
\newblock Utilisation de La Haute Resolution Spectrale Pour Suivre l'etat Des
  Couverts Vegetaux.
\newblock  In \emph{Spectral Signatures of Objects in Remote Sensing}; Guyenne, T.D.,
  Hunt, J.J., Eds.;  {ESA Special Publication}: 1988; Aussois, France, Volume 287, p. 279.

@@

\bibitem[Vincini \em{et~al.}(2006)Vincini, Frazzi, and D'Alessio]{vincini2006}
Vincini, M.; Frazzi, E.; D'Alessio, P.
\newblock Angular Dependence of Maize and Sugar Beet {{VIs}} from Directional
  {{CHRIS}}/{{Proba}} Data.
\newblock  In Proceedings of the 4th {{ESA CHRIS PROBA}} Workshop,  Frascati, Italy, 19--21 September 2006; Volume 2006, pp.
  19--21.

>>>>

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0003-0748-6624} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-7834-4717} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0003-2567-8689} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorD}{0000-0002-6390-5873} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorE}{0000-0001-6002-6980} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorF}{0000-0001-6640-679X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{\hl{Patrick Schratz} %MDPI: Please carefully check the accuracy of names and affiliations.
 $^{1,}$*\orcidA{}, \hl{Jannes Muenchow} %MDPI: This author is different from redmine, please confirm.
 $^{1}$\orcidB{}, Eugenia Iturritxa $^{2}$\orcidD{}, José Cortés $^{1}$\orcidC{}, Bernd Bischl $^{3}$\orcidE{} and~Alexander~Brenning $^{1}$\orcidF{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad \hl{GIScience Group,} %MDPI: Please check if the addresses are arranged from small to large. The same to aff. 3.
 Department of Geography, Friedrich Schiller University Jena, \hl{Germany;} %MDPI: please add city and post code. The same to affs. 2 and 3.
 malnamalja@gmx.de~(J.M.); jose.cortes@uni-jena.de~(J.C.); alexander.brenning@uni-jena.de~(A.B.)\\
$^{2}$ \quad \hl{NEIKER} %MDPI: please check if this address is correct.
 Tecnalia, \hl{Spain;} eiturritxa@neiker.eus\\
$^{3}$ \quad \hl{Computational Statistics Group,} Department of Statistics, Ludwig-Maximilians-Universität München, \hl{Germany;} bernd.bischl@stat.uni-muenchen.de
}

@@

The \textit{Pinus radiata} plots of this study, namely Laukiz1, Laukiz2, Luiando, and Oiartzun, are located in the northern part of the Basque Country (Figure~\ref{fig:study_area}).
Oiartzun has the largest number of observations ($n = 559$ trees), while Laukiz2 is the largest in area (1.44~ha).
All plots besides Luiando are located within 100~km from the coast (Figure~\ref{fig:study_area}).
A total of 1808~observations are available (Laukiz1: 559, Laukiz2: 451, Luiando: 301, Oiartzun: 497).
Field surveys were conducted in September 2016 by experienced forest pathologists.
Defoliation was measured in 5\% steps through visual inspection with the help of a score card.
For Laukiz2, values at three height levels (bottom, mid, and top) were available and averaged into an overall defoliation value, resulting in values that are not multiples of 5\% (e.g., 8.33\%).
The magnitude of human observer errors in such surveys, including the present one, is not precisely known and has being discussed for many years~\cite{innes1993}.
\hl{Ref.}%MDPI: Reference citation can't be in the begining of sentence, we add Ref., please confirm.
~\cite{maclean1982} estimated human observer errors in defoliation surveys to range between 7\% and 18\%.

@@

In total, the benchmarking grid consisted of 156 experiments (6 feature sets $\times$ 3~ML algorithms $\times$ 8 feature-selection methods and for the L1/L2 models, 6 feature sets~$\times$~2~models.
The selected hyperparameter settings are shown in Appendix~\ref{appendixA} Table~\ref{tab:hyperparameter_limits}.
All code and data are included in the research compendium of this study (\url{https://doi.org/10.5281/zenodo.2635403}, \hl{accessed on).} %MDPI: Please add access date after the URL; like “http://xxxxxxx (access on 8 January 2021)”, please check all URL in manuscript and add the specific date.

@@

The algorithm implementations of the following packages were used: xgboost~\cite{chen2016} (\textit{\hl{Extreme Gradient Boosting}}), %MDPI: Is the italic necessary?
 kernlab~\cite{kernlab} (support vector machine)m and glmnet~\cite{glmnet} (penalized regression).
The filter implementations of the following packages were used: praznik~\cite{praznik} and FSelectorRcpp~\cite{fselectorrcpp}.
Package mlr~\cite{mlr} was used for all modeling related steps, and
drake~\cite{drake} was used for structuring the work and for reproducibility.
This study is available as a research compendium on Zenodo (\url{10.5281/zenodo.2635403}, \hl{accessed on).} %MDPI: Please add access date after the URL; like “http://xxxxxxx (access on 8 January 2021)”, please check all URL in manuscript and add the specific date.
Apart from the availability of code and manuscript sources, a static webpage is available at (\url{https://pat-s.github.io/2019-feature-selection}, \hl{accessed on),} %MDPI: Please add access date after the URL; like “http://xxxxxxx (access on 8 January 2021)”, please check all URL in manuscript and add the specific date.
which includes additional side analyses that were carried out during the creation of this study.

@@

% - RMSE around 27
% - MBO tuned penalized methods are substantially worse
Overall, the response variable \enquote{tree defoliation} could be modeled with an \ac{RMSE} of 28 percentage points (p.p.) (Figure~\ref{fig:perf-result}).
SVM showed almost no differences in RMSE across feature sets whereas other learners (RF, SVM, XGBoost, lasso and ridge) differed up to five p.p. (Figure~\ref{fig:perf-result}).
SVM showed the best overall performance with a mean difference of around three p.p. to the next best model (XGBoost) (\hl{Table}%MDPI: we adjust the order of Tables 3, 4 and Tables 5, 6, please confirm.
~\ref{tab:best-learner-perf}).
Performance differences between test folds were large: Predicting on Luiando resulted in an RMSE of 9.0 p.p. for learner SVM (without filter) but up to 54.3 p.p. when testing on Laukiz2 (Table~\ref{tab:svm-single-fold-perf}).

@@

\institutionalreview{\hl{ } %MDPI: In this section, please add the Institutional Review Board Statement and approval number for studies involving humans or animals. Please note that the Editorial Office might ask you for further information. Please add ``The study was conducted according to the guidelines of the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).'' OR ``Ethical review and approval were waived for this study, due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans or animals. You might also choose to exclude this statement if the study did not involve humans or animals.
}

\informedconsent{\hl{ } %MDPI: Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.
}

\dataavailability{The data presented in this study are openly available in Zenodo at \url{https://doi.org/10.5281/zenodo.2635403} \hl{(accessed on).} %MDPI: Please add access date after the URL; like “http://xxxxxxx (access on 8 January 2021)”, please check all URL in manuscript and add the specific date.
}

% \acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

@@

		\bfseries{Name} & \bfseries{Formula}                                                                                   & \bfseries{Reference~\hl{*}} %MDPI: there is no explanation for *.

@@

		GDVI            & $(R_{800}^n-R_{680}^n) / (R_{800}^n+R_{680}^n)$ \hl{**                                                   } %MDPI: there is no explanation for **.
 &~\cite{wu2014}                 \\

@@

\bibitem[Thenkabail \em{et~al.}(2018)Thenkabail, Lyon, and
  Huete]{thenkabail2018}
Thenkabail, P.S.; Lyon, J.G.; Huete, A. (Eds.)
\newblock {\em Hyperspectral Indices and Image Classifications for Agriculture
  and Vegetation}; {CRC Press}:  \hl{Boca Raton, FL, USA,} %newly added information, please confirm
 2018, doi:10.1201/9781315159331.

@@

\bibitem[Lin \em{et~al.}(2014)Lin, Yan, Wang, and Song]{lin2014}
Lin, H.; Yan, E.; Wang, G.; Song, R.
\newblock Analysis of Hyperspectral Bands for the Health Diagnosis of Tree
  Species.
\newblock  In Proceedings of the 2014 {{Third International Workshop}} on {{Earth Observation}} and
  {{Remote Sensing Applications}} ({{EORSA}}),  \hl{Changsha, China, 11--14 June} %MDPI: newly added, please confirm. The same to refs. 37, 45, 56, 63, 87, 89, 145
 2014; pp. 448--451, doi:10.1109/EORSA.2014.6927931.

@@

\bibitem[Trunk(1979)]{trunk1979}
Trunk, G.V.
\newblock A {{Problem}} of {{Dimensionality}}: A {{Simple Example}}.
\newblock {\em IEEE Trans. Pattern Anal. Mach. Intell.}
  {\bf 1979}, {\em \hl{PAMI-1}}, %MDPI: please confirm if this volume is correct.
 306--307.

@@

\bibitem[Innes(1993)]{innes1993}
Innes, J.
\newblock Methods to Estimate Forest Health.
\newblock {\em Silva Fenn.} {\bf 1993}, {\em \hl{27}}, %MDPI: please add page.
 doi:10.14214/sf.a15668.

@@

\bibitem[Das(2001)]{das2001}
Das, S.
\newblock \emph{Filters, {{Wrappers}} and a {{Boosting}}-{{Based Hybrid}} for
  {{Feature Selection}}};
\newblock  \hl{{{ICML}}:} %MDPI: please add location of publisher. The same to refs. 39, 45, 56, 62, 76, 125, 142
  2001.

@@

\bibitem[Dietterich(2000)]{dietterich2000}
Dietterich, T.G.
\newblock Ensemble {{Methods}} in {{Machine Learning}}.
\newblock  In Proceedings of the {{First International Workshop}} on {{Multiple
  Classifier Systems}}, \hl{Cagliari, Italy, 21--23 June} 2000; {Springer}:  \hl{Berlin/Heidelberg, Germany,} %newly added information, please confirm
 2000; pp. 1--15.

@@

\bibitem[Feurer \em{et~al.}(2015)Feurer, Klein, Eggensperger, Springenberg,
  Blum, and Hutter]{feurer2015}
Feurer, M.; Klein, A.; Eggensperger, K.; Springenberg, J.; Blum, M.; Hutter, F.
\newblock Efficient and {{Robust Automated Machine Learning}}. In {\em Advances
  in {{Neural Information Processing Systems}} 28}; Cortes, C., Lawrence, N.D.,
  Lee, D.D., Sugiyama, M., Garnett, R., Eds.; {\hl{Curran Associates, Inc.}}:  2015;
  pp. 2962--2970.

@@

\bibitem[Zuber and Strimmer(2011)]{zuber2011}
Zuber, V.; Strimmer, K.
\newblock High-{{Dimensional Regression}} and {{Variable Selection Using CAR
  Scores}}.
\newblock {\em Stat. Appl. Genet. Mol. Biol.} {\bf
  2011}, {\em \hl{10}}. %MDPI: please add page. The same to ref. 69

\bibitem[Kira and Rendell(1992)]{kira1992}
Kira, K.; Rendell, L.A.
\newblock The Feature Selection Problem: Traditional Methods and a New
  Algorithm.
\newblock  In Proceedings of the Tenth National Conference on {{Artificial}}
  Intelligence, \hl{San Jose, CA, USA, 12--16 July} 1992; {\hl{AAAI Press}}:  1992; pp. 129--134.

@@

\bibitem[Brenning(2012)]{sperrorest}
Brenning, A.
\newblock Spatial Cross-Validation and Bootstrap for the Assessment of
  Prediction Rules in Remote Sensing: The {{R}} Package Sperrorest.
\newblock  In Proceedings of the 2012 {{IEEE International Geoscience}} and {{Remote Sensing
  Symposium}}, \hl{Munich, Germany, 22--27 July} 2012; {R} Package Version 2.1.0; {\hl{IEEE}}:  2012,
\newblock
  doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/igarss.2012.6352393}{\detokenize{10.1109/igarss.2012.6352393}}}.

@@

\bibitem[Molnar(2019)]{molnar2019}
Molnar, C.
\newblock {\em Interpretable Machine Learning---{{A Guide}} for {{Making Black
  Box Models Explainable}}};  \hl{2019.} %MDPI: please add publisher and location. The same to ref. 66, 67, 74, 100

@@

\bibitem[{R Core Team}(2019)]{rcoreteam2019}
{R Core Team}.
\newblock {\em R: A {{Language}} and {{Environment}} for {{Statistical
  Computing}}};  \hl{R Core Team:} 2019.

\bibitem[Chen and Guestrin(2016)]{chen2016}
Chen, T.; Guestrin, C.
\newblock {{XGBoost}}: A {{Scalable Tree Boosting System}}.
\newblock  In Proceedings of the {{22nd ACM SIGKDD International Conference}} on
  {{Knowledge Discovery}} and {{Data Mining}}, {{KDD}} '16, \hl{San Francisco, CA, USA, 13--17 August} 2016; {ACM}: {New York, NY, USA},
  2016; pp. 785--794, doi:10.1145/2939672.2939785.

@@

\bibitem[Kursa(2018)]{praznik}
Kursa, M.B.
\newblock {\em Praznik: Collection of {{Information}}-{{Based Feature Selection
  Filters}}};  \hl{2018.}

\bibitem[Zawadzki and Kosinski(2019)]{fselectorrcpp}
Zawadzki, Z.; Kosinski, M.
\newblock {\em {{FSelectorRcpp}}: '{{Rcpp}}' {{Implementation}} of
  '{{FSelector}}' {{Entropy}}-{{Based Feature Selection Algorithms}} with a
  {{Sparse Matrix Support}}};  \hl{2019.}

@@

\bibitem[Landau(2018)]{drake}
Landau, W.M.
\newblock The Drake {{R}} Package: A Pipeline Toolkit for Reproducibility and
  High-Performance Computing.
\newblock {\em J. Open Source Softw.} {\bf 2018}, {\em \hl{3}}.

@@

\bibitem[Lehnert \em{et~al.}(2016)Lehnert, Meyer, and Bendix]{lehnert2016}
Lehnert, L.W.; Meyer, H.; Bendix, J.
\newblock {\em Hsdar: Manage, Analyse and Simulate Hyperspectral Data in
  {{R}}};  \hl{2016.}

@@

\bibitem[Rengarajan and Schott(2016)]{rengarajan2016}
Rengarajan, R.; Schott, J.R.
\newblock Modeling Forest Defoliation Using Simulated {{BRDF}} and Assessing
  Its Effect on Reflectance and Sensor Reaching Radiance.
\newblock  In \emph{Remote {{Sensing}} and {{Modeling}} of {{Ecosystems}} for
  {{Sustainability XIII}}}; {\hl{International Society for Optics and Photonics}}:
  2016; Volume 9975, p. 997503, doi:10.1117/12.2235391.

@@

\bibitem[Rochac and Zhang(2016)]{rochac2016}
Rochac, J.F.R.; Zhang, N.
\newblock Feature Extraction in Hyperspectral Imaging Using Adaptive Feature
  Selection Approach.
\newblock  In Proceedings of the 2016 {{Eighth International Conference}} on {{Advanced Computational
  Intelligence}} ({{ICACI}}),  \hl{Chiang Mai, Thailand, 14--16 February} 2016; pp. 36--40, doi:10.1109/ICACI.2016.7449799.

@@

\bibitem[Keller \em{et~al.}(2016)Keller, Braun, Hinz, and Weinmann]{keller2016}
Keller, S.; Braun, A.C.; Hinz, S.; Weinmann, M.
\newblock Investigation of the Impact of Dimensionality Reduction and Feature
  Selection on the Classification of Hyperspectral {{EnMAP}} Data.
\newblock  In Proceedings of the 2016 8th {{Workshop}} on {{Hyperspectral Image}} and {{Signal
  Processing}}: Evolution in {{Remote Sensing}} ({{WHISPERS}}),  \hl{Los Angeles, CA, USA, 21--24 August} 2016; pp.
  1--5, doi:10.1109/WHISPERS.2016.8071759.

@@

\bibitem[Walthall \em{et~al.}(1994)Walthall, Daughtry, Chappelle, Mcmurtrey,
  and Kim]{walthall1994}
Walthall, C.L.; Daughtry, C.S.T.; Chappelle, E.W.; Mcmurtrey, J.E.; Kim, M.S.
\newblock \emph{The {{Use}} of {{High Spectral Resolution Bands}} for {{Estimating
  Absorbed Photosynthetically Active Radiation}} ({{A Par}})}; { \hl{1994}}.

@@

\bibitem[Chen(1996)]{chen1996}
Chen, J.M.
\newblock \emph{Evaluation of Vegetation Indices and a {{Modified Simple Ratio}} for
  Boreal Applications};
\newblock Technical Report; {\hl{Natural Resources Canada/ESS/Scientific and
  Technical Publishing Services}}:  1996, doi:10.4095/218303.

@@

\bibitem[Guyot and Baret(1988)]{guyot1988}
Guyot, G.; Baret, F.
\newblock Utilisation de La Haute Resolution Spectrale Pour Suivre l'etat Des
  Couverts Vegetaux.
\newblock  In \emph{Spectral Signatures of Objects in Remote Sensing}; Guyenne, T.D.,
  Hunt, J.J., Eds.;  {\hl{ESA Special Publication}}: 1988; Volume 287, p. 279.

@@

\bibitem[Vincini \em{et~al.}(2006)Vincini, Frazzi, and D'Alessio]{vincini2006}
Vincini, M.; Frazzi, E.; D'Alessio, P.
\newblock Angular Dependence of Maize and Sugar Beet {{VIs}} from Directional
  {{CHRIS}}/{{Proba}} Data.
\newblock  In Proceedings of the 4th {{ESA CHRIS PROBA}} Workshop,  \hl{Frascati, Italy, 19--21 September} 2006; Volume 2006, pp.
  19--21.
